---
title: "Homework 4"
author: "Wenjia Xie"
date: "March 8, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem One
## (1)
```{r}
uni <- c(0.42,0.38,0.48,0.11,0.30,0.06,0.78,0.35,0.29,0.23,0.88,0.71,0.16, 0.79,0.01,0.40,0.57,0.22,0.75,0.41,0.90,0.66,0.08,0.82,0.09)
ks.test(uni,"punif")
```
                                                                            Since the p-value here is 0.3501, we can not reject the null hypothesis. The data is distributed as a uniform distribution.                 

## (2)
```{r}
x <- seq(-1,1,0.01)
fx <- ifelse(x > 0 & x <=0.5, 2/3,
   ifelse(x > 0.5 & x < 1,  0.5, 0))
ks.test(uni,fx)

```

The p-value is so small that we reject the null hypothesis.Thus,the data is not distributed as fx.

## (3)


# Problem Two
```{r}
normal <- c(25.088,26.615,25.468,27.453,23.845,
25.996,26.516,28.240,25.980,30.432,
26.560,25.844,26.964,23.382,25.282,
24.432,23.593,24.644,26.849,26.801,
26.303,23.016,27.378,25.351,23.601,
24.317,29.778,29.585,22.147,28.352,
29.263,27.924,21.579,25.320,28.129,
28.478,23.896,26.020,23.750,24.904,
24.078,27.228,27.433,23.341,28.923,
24.466,25.153,25.893,26.796,24.743)
ks.test(normal,"pnorm",26,2)
qqnorm(normal)
qqline(normal, col = "steelblue", lwd = 2)
hist(normal)
plot(density(normal))
```

The p-value is large enough and we do not have sufficient evidence to rejuct the null hypothesis.From the qqplot,histgram and density plot, we can also draw the same conclusion that these data come from normal distribution. 

# Problem Three
```{r}
X <- c(0.61,0.29,0.06,0.59,−1.73,
−0.74,0.51,−0.56,−0.39,1.64,
0.05,−0.06,0.64,−0.82,0.31,
1.77,1.09,−1.28,2.36,1.31,
1.05,−0.32,−0.40,1.06,−2.47)

Y <- c(2.20,1.66,1.38,0.20,
0.36,0.00,0.96,1.56,
0.44,1.50,−0.30,0.66,
2.31,3.29,−0.27,−0.37,
0.38,0.70,0.52,−0.71)

ks.test(X,Y)
ks.test(X+2,Y)
```

Using ks.test, we can find that X and Y are from the same distribution. However, X+2 and Y are not from the same distribution.

# Problem Four

```{r}
data4 <- readRDS("norm_sample.Rdata")
ks.test(data4,"pnorm")
```

```{r}
set.seed(1)
ecdf(data4)
standnorm <-rnorm(n = length(data4),mean = 0,sd = 1)
diff <- sort(data4)-sort(standnorm)
D <- max(abs(diff))
```


# problem Five
```{r}
fiji<-read.table("fijiquakes.dat",header = T)
mag<-fiji$mag
Fn <- ecdf(mag)
library(Hmisc)
total<-sum( (mag<=4.9) & (mag>4.3))
binconf(total,length(mag),method="wilson",0.05)

```


The 95% for F(4.9) − F(4.3) is [0.50,0.56].


```{r}
faith<-read.table("faithful.dat",skip = 25)
waiting<-faith$waiting
avg<-mean(waiting)
var<-var(waiting)
n<-length(waiting)
L<-round(avg-qnorm(0.95)*sqrt(var/n),2)
U<-round(avg+qnorm(0.95)*sqrt(var/n),2)

print(paste("the 90% CI for mean waiting time is:[",L,",",U,"]"))

median(waiting)

```

For the faithful data, the 90 percent confidence interval for the mean waiting time is [69.54,72.25]. The median of the waiting time is 76. 